---
title: "proplogix_jobs_report"
output: html_document
---
```{r}
library(rgdal)    # for readOGR and others
library(sp)       # for spatial objects
library(leaflet)  # for interactive maps (NOT leafletR here)
library(dplyr)    # for working with data frames
library(ggplot2)  # for plotting
library(data.table)# for easy data manipulation
library(acs)
library(stringr)
library(stringdist)
library(choroplethr) # for maps
library(choroplethrMaps)
library(scales)
library(Amelia)
library(splitstackshape) #for data.table friendly string splitting
#devtools::install_github("dgrtwo/gganimate")
library(gganimate)
library(viznetwork)
#options(scipen=999)
```

########################################
## proplogix scraped deed final_data  ##
########################################

```{r}
file <- fread("C:/Users/trobart/Desktop/Deeds/final_deed_data/final_data7.csv")
nrow(file)
names(file)[3] <- "Parcel ID Number"
# title agent explicit munging
#removing unwanted parts of title agent

file[`Title Agent`  %like%  "p. a.", `Title Company` := `Title Agent`]
file[`Title Agent`  %like%  "p. l.", `Title Company` := `Title Agent`]
file[`Title Agent`  %like%  "p.a.",  `Title Company` := `Title Agent`]
file[`Title Agent`  %like%  "p.l.",  `Title Company` := `Title Agent`]
file[`Title Agent`  %like%  "pl",    `Title Company` := `Title Agent`]
file[`Title Agent`  %like%  "pllc",  `Title Company` := `Title Agent`]
file[`Title Agent`  %like%  "inc.",  `Title Company` := `Title Agent`]
file[`Title Agent`  %like%  "llc",   `Title Company` := `Title Agent`]

file[`Title Agent`  %like% "p. a.",  `Title Company` := `Title Agent`]
file[`Title Agent`  %like% "p. l.",  `Title Company` := `Title Agent`]
file[`Title Agent`  %like% "p.a.",   `Title Company` := `Title Agent`]
file[`Title Agent`  %like% "p.l.",   `Title Company` := `Title Agent`]
file[`Title Agent`  %like% "pllc",   `Title Company` := `Title Agent`]
file[`Title Agent`  %like% "inc.",   `Title Company` := `Title Agent`]
file[`Title Agent`  %like% "llc",    `Title Company` := `Title Agent`]
file[`Title Agent`  %like% "title",  `Title Company` := `Title Agent`]


file[,`Title Agent` := gsub(" esquire","", tolower(`Title Agent`))]
file[,`Title Agent` := gsub(" attorney at law","", tolower(`Title Agent`))]
file[,`Title Agent` := gsub(" attorney","", tolower(`Title Agent`))]
file[,`Title Agent` := gsub(" an employee of","", tolower(`Title Agent`))]
file[,`Title Agent` := gsub(" esq.","", tolower(`Title Agent`))]
file[,`Title Agent` := gsub(" esq","", tolower(`Title Agent`))]
file[,`Title Agent` := gsub("attn ","", tolower(`Title Agent`))]
file[,`Title Agent` := gsub("attn","", tolower(`Title Agent`))]


file[,`Title Agent` := gsub("[^[:alnum:] ]", "", tolower(`Title Agent`))]

#company explicit munging
file[,`Title Company` := gsub(" esquire","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" attorney at law","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" attorney","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" an employee of","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" esq.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" esq","", tolower(`Title Company`))]
file[,`Title Company` := gsub("attn ","", tolower(`Title Company`))]
file[,`Title Company` := gsub("attn","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", p. a.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", p. l.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", p.a.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", p.l.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", pl","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", pllc","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", inc.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(", llc","", tolower(`Title Company`))]

file[,`Title Company` := gsub(" p. a.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" p. l.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" p.a.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" p.l.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" pllc","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" inc.","", tolower(`Title Company`))]
file[,`Title Company` := gsub(" llc","", tolower(`Title Company`))]

file[,`Title Company` := gsub("[^[:alnum:] ]", "", tolower(`Title Company`))]
```

#######################################################
### Loading and munging proplogix job records data  ###
#######################################################

```{r}
prop_jobs <- fread("C:/Users/trobart/Downloads/tannersRequest.csv")
missmap(prop_jobs)
nrow(prop_jobs)


prop_jobs <- cSplit(prop_jobs, "Agency", "- ")
prop_jobs[!is.na(Agency_3),Agency_2 := Agency_3]
prop_jobs[,Location := Agency_2]
prop_jobs[,Agency := Agency_1]
prop_jobs[,c("Agency_1","Agency_2", "Agency_3") := NULL]

#munging special formatting characters out
prop_jobs[,`Agent` := gsub("[^[:alnum:] ]","", tolower(`Agent`))]
prop_jobs[,`Agency` := gsub("[^[:alnum:] ]","", tolower(`Agency`))]
prop_jobs[,`PropertyId` := gsub("[^[:alnum:] ]","", `PropertyId`)]
prop_jobs[,`PropertyId` := gsub(" ","", `PropertyId`)]


agents <- tolower(unique(prop_jobs$Agent))
agencies <- tolower(unique(prop_jobs$Agency))


prop_all_title_names <- unique(append(agents, agencies))
length(prop_all_title_names) #1869 unique client individuals and companies

```
## remove and replace duplicate entries with the shortest version
```{r}
for (i in 1:length(prop_all_title_names)){
  if (length(prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]]) > 1){
    print("boop")
    shorter <- min(prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]])
    prop_jobs[`Agency` %in% prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]], `Agency` := shorter]
    prop_jobs[`Agent` %in% prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]], `Agent` := shorter]
  }
}


agents <- tolower(unique(prop_jobs$Agent))
agencies <- tolower(unique(prop_jobs$Agency))
prop_all_title_names <- unique(append(agents, agencies))
length(prop_all_title_names) #1828 unique client individuals and companies after correcting duplicates

#pure intersection of prop records and deed data
intersect_title_agents <- intersect(prop_all_title_names, file$`Title Agent`) #note right now this is just hillsborough
intersect_title_companies <- intersect(prop_all_title_names, file$`Title Company`)

intersect_title_agents
intersect_title_companies

# Hillsborough only agents and agencies in prop data 
hills_agents <- tolower(unique(prop_jobs[County == "Hillsborough"]$Agent))
hills_agencies <- tolower(unique(prop_jobs[County == "Hillsborough"]$Agency))
hills_all_title_names <- unique(append(hills_agents, hills_agencies))


length(hills_all_title_names)
```

##########################################################
### sorting and evaluation of usable/missing deed data ###
##########################################################


#### Title Agent/ Company ####

```{r}
# missing data counts and map
missmap(file)
1- length(file$`Title Agent`[ file$`Title Agent` == ""])/nrow(file) # currently 54.9% present data for title agent
1- length(file$`Title Company`[ file$`Title Company` == ""])/nrow(file) # currently 7% present data for title company 
1- length(file$`Parcel ID Number`[ file$`Parcel ID Number` == ""])/nrow(file) # currently .74% present data for parcel ID
### removing missing ###

reduced <- file[`Title Agent` != "",] # leaves 27144 records in our test case
parcel_reduced <- file[`Parcel ID Number` != "",]

#sorting for largest counts of title agent
title_agents_count <- sort(table(reduced$`Title Agent`),decreasing = TRUE)
title_company_count <- sort(table(reduced$`Title Company`),decreasing = TRUE)

summary(title_agents_count)# 27564 cases
nrow(title_agents_count) #7876 unique values

summary(title_company_count)# 3615 cases
nrow(title_company_count) #463 unique values

#quick look at top 10
title_agents_count[0:10]
title_company_count[0:10]


deed_agents <- tolower(unique(reduced$`Title Agent`))
deed_agencies <- tolower(unique(reduced$`Title Agency`))


deed_all_title_names <- unique(append(deed_agents, deed_agencies))
length(deed_all_title_names)


for (i in 1:length(prop_all_title_names)){
  if (length(deed_all_title_names[deed_all_title_names %like% prop_all_title_names[i]]) > 1){
    print("boop")
    shorter <- min(deed_all_title_names[deed_all_title_names %like% prop_all_title_names[i]])
    reduced[`Title Company` %like% prop_all_title_names[i], `Title Company` := shorter]
    reduced[`Title Agent` %like% prop_all_title_names[i], `Title Agent` := shorter]
  }
}

deed_agents <- tolower(unique(reduced$`Title Agent`))
deed_agencies <- tolower(unique(reduced$`Title Agency`))


deed_all_title_names <- unique(append(deed_agents, deed_agencies))
length(deed_all_title_names)
```

############################
## Parcel ID evaluation ###
############################

###Unique property counts
```{r}
unique_prop_parcels <- unique(prop_jobs$PropertyId)
hills_prop_parcels <- unique(prop_jobs[County == "Hillsborough"]$PropertyId) #unique prop hillsborough parcel IDs

length(prop_jobs$PropertyId) #Total   - 69380
length(unique_prop_parcels)  #Uniques - 58224

length(unique_prop_parcels)/length(prop_jobs$PropertyId) # ~84% Unique proplogix properties within proplogix jobs
length(hills_prop_parcels)/length(unique_prop_parcels) # ~13.5% of unique proplogix parcels come from Hillsbrough



nrow(reduced[`Parcel ID Number` == ""])/nrow(reduced) # 22.8% of parcel ID are missing currently when 

sort(table(reduced[`Parcel ID Number` %in% unique_prop_parcels]$`Parcel ID Number`), decreasing =  T)

length(unique(reduced[`Parcel ID Number` %in% unique_prop_parcels]$`Parcel ID Number`)) #1533 unique parcel IDs in deed data matched to prop data


#proportion of unique properties in the prop data out of the total observed deed data.
length(unique(reduced[`Parcel ID Number` %in% unique_prop_parcels]$`Parcel ID Number`))/length(unique(reduced$`Parcel ID Number`)) # ~8.5%

#Hillsborough only

sort(table(reduced[`Parcel ID Number` %in% hills_prop_parcels]$`Parcel ID Number`), decreasing =  T)

length(unique(reduced[`Parcel ID Number` %in% hills_prop_parcels]$`Parcel ID Number`)) #1533 unique parcel IDs in deed data matched to prop data


#proportion of unique properties in the prop data out of the total observed deed data.
length(unique(reduced[`Parcel ID Number` %in% hills_prop_parcels]$`Parcel ID Number`))/length(unique(reduced$`Parcel ID Number`))


###################################
# Levenshtein Distance Clustering # Defunct - vector too large for adist
###################################
# 
# d  <- adist(reduced$`Title Agent`)
# rownames(d) <- reduced$`Title Agent`
# hc <- hclust(as.dist(d))
# plot(hc) #this is a mess with so many clusters
# 
# 
# ### cluster based on tree height differences ###
# num.height <- 0.5 # at least half tree height for cluster to be unique
# p <- cutree(hc, h = num.height)
# plot(p)
# 
# 
# title_agent_clusters <- data.frame(names = reduced$`Title Agent`, group.prob = p)
# title_company_clusters <- data.frame(names = reduced$`Title Company`, group.prob = p)


#####################################################################
### alternate method for clustering based on agrep self-groupings ###
#####################################################################

agent_groups <- list()
x <- reduced$`Title Agent`
i <- 1

while(length(x) > 0){
  
  if (nchar(x[1]) > 5) { 
    id <- agrep(x[1], x, ignore.case = TRUE, max.distance = 0.15)
    agent_groups[[i]] <- x[id]
    x <- x[-id]
  }
  else {
    agent_groups[[i]] <- x[1]
    x <- x[-1]
  }
  i <- i + 1
}

head(agent_groups)
tail(agent_groups)



#picking the most common name within a cluster, and creating a set of those primary names
deeds_primary_title_names <- list()

for (i in 1:length(agent_groups)){
  deeds_primary_title_names <- c(deeds_primary_title_names, names(sort(table(agent_groups[[i]]), decreasing = TRUE)[1]))}
deeds_primary_title_names <- unlist(deeds_primary_title_names)

for (i in 1:length(agent_groups)){
  names(agent_groups[[i]]) <- names(sort(table(agent_groups[[i]]), decreasing = TRUE)[1])}

head(deeds_primary_title_names, 100)


#######################################################################
### Linking Proplogix Records ###
#######################################################################


########################################################
### testing deed and prop record matching with dplyr ###
########################################################

wordlist <- expand.grid(words = deeds_primary_title_names , ref = prop_all_title_names, stringsAsFactors = FALSE)
matches <- wordlist %>% group_by(words) %>% mutate(match_score = 1-stringdist(words, ref, method = 'jw')) %>%
  summarise(match = match_score[which.max(match_score)], matched_to = ref[which.max(match_score)])

matches <- data.table(matches)
matches[match > .87]

################################################################
# testing %like% agent name matching of deed and prop records  #
################################################################

like_agent_matched_records <- data.table()


for (i in 1:length(prop_all_title_names)){
  if (nrow(reduced[`Title Agent` %like% prop_all_title_names[i]]) != 0){
    like_agent_matched_records <- rbind(like_agent_matched_records, reduced[`Title Agent` %like% prop_all_title_names[i]])
    #reduced[`Title Agent` %in% prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]], `Title Agent` := shorter]
    
  }
}

like_agent_matched_records #2143


### Hillsborough specific version of above agent matching

hills_agent_matched_records <- data.table()


for (i in 1:length(hills_all_title_names)){
  if (nrow(reduced[`Title Agent` %like% hills_all_title_names[i]]) != 0){
    hills_agent_matched_records <- rbind(hills_agent_matched_records, reduced[`Title Agent` %like% hills_all_title_names[i]])
    #reduced[`Title Agent` %in% prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]], `Title Agent` := shorter]
    
  }
}

hills_agent_matched_records #1805

######################################################
# matching records by parcel ID                     ##
######################################################

parcel_matched_records <- data.table()

for (i in 1:length(unique_prop_parcels)){
  if (nrow(parcel_reduced[`Parcel ID Number` %in% unique_prop_parcels[i]]) != 0){
    
    parcel_matched_records <- rbind(like_parcel_matched_records, parcel_reduced[`Parcel ID Number` %in% unique_prop_parcels[i]])
    #reduced[`Title Agent` %in% prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]], `Title Agent` := shorter]
    
  }
}

parcel_matched_records


#aggregating the parcel # matching and the agent name matching
all_matched_records <- unique(merge(parcel_matched_records, like_agent_matched_records, all = T))
all_matched_records

########################################################################
#following is Hillsborough exclusive of the above parcel matching code #
########################################################################

hills_parcel_matched_records <- data.table()

for (i in 1:length(hills_prop_parcels)){
  if (nrow(parcel_reduced[`Parcel ID Number` %in% hills_prop_parcels[i]]) != 0){
    
    hills_parcel_matched_records <- rbind(like_parcel_matched_records, parcel_reduced[`Parcel ID Number` %in% hills_prop_parcels[i]])
    #reduced[`Title Agent` %in% prop_all_title_names[prop_all_title_names %like% prop_all_title_names[i]], `Title Agent` := shorter]
    
  }
}

hills_parcel_matched_records #2777


hills_matched_records <- unique(merge(hills_parcel_matched_records, hills_agent_matched_records, all = T))
hills_matched_records #3746


hills_matched_counts <- as.data.frame(sort(table(hills_matched_records$`Title Agent`), decreasing = T)[2:22])
hills_matched_counts


## testing replacing original records with matched values ##

test <- reduced
test_match <- data.table()

for (i in 1:length(prop_jobs$PropertyId)){
  if (nrow(test[`Parcel ID Number` %in% unique_prop_parcels]) != 0){
    test_match <- rbind( test_match, test[`Parcel ID Number` == prop_jobs$PropertyId[i]]$`Parcel ID Number`) #, `Title Agent` := names(agent_groups[[j]][1])]
    #test$`Title Agent`[i] <- names(agent_groups[[j]][1])
    #matches[words == names(sort(table(agent_groups[[j]]), decreasing = TRUE)[1])]$matched_to
  }
}
test_match

```
#########################
# Plotting and Viz  ###
#########################

###########################
###    PROPLOGIX DATA
###########################


##############################################
##### Title Agent/Agency quantification ######


#######################################
####          All PropLogix Data       ####

##### plot of top 20 client agents by jobs in proplogix data

```{r}
prop_agent_counts <- as.data.frame(sort(table(prop_jobs$Agent), decreasing = T)[2:21]) #first element is stewart title, an agency, so exlcuded and moved to next plot

ggplot(data = prop_agent_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=25 )) +
  labs(x = "Proplogix Client Agents", y = "# of records in Proplogix data") +
  ggtitle("Top 20 Agents by raw Proplogix job volume")

## plot of top 20 client agencies by their job counts with proplogix

prop_agency_counts <- as.data.frame(sort(table(prop_jobs$Agency), decreasing = T)[1:20])

ggplot(data = prop_agency_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=25)) +
  labs(x = "Proplogix Client Agencies", y = "# of records in Proplogix data") +
  ggtitle("Top 20 Agencies by raw Proplogix job volume")


## count of most agents per agency in prop data

prop_agents_per_agency <- setorder(prop_jobs[, .(number_of_agents = uniqueN(Agent)), by = Agency], -number_of_agents)


ggplot(data = prop_agents_per_agency, aes(x= Agency, y = number_of_agents, order)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=25 )) +
  labs(x = "Agencies", y = "# of Agents in Proplogix data") +
  ggtitle("Top 20 Agencies by # of Agents seen in Proplogix data") +
  scale_x_discrete(limits = prop_agents_per_agency$Agency[1:20])



```

###############################################
#####        Hillsborough Only   ############


## plot of top 20 agents by jobs in proplogix data
```{r}
prop_hills_agent_counts <- as.data.frame(sort(table(prop_jobs[County == "Hillsborough"]$Agent), decreasing = T)[1:20])

ggplot(data = prop_hills_agent_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=25 )) +
  labs(x = "Hillsborough Agents", y = "# of records in Proplogix data") +
  ggtitle("Top 20 Hillsborough Agents by raw Proplogix job volume")

## plot of top 20 client agencies by their job counts with proplogix

prop_hills_agency_counts <- as.data.frame(sort(table(prop_jobs[County == "Hillsborough"]$Agency), decreasing = T)[1:20])

ggplot(data = prop_hills_agency_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=25 )) +
  labs(x = "Hillsborough Agencies", y = "# of records in Proplogix data") +
  ggtitle("Top 20 Hillsborough Agencies by raw Proplogix job volume")


## count of most agents per agency in prop data

hills_agents_per_agency <- setorder(prop_jobs[County == "Hillsborough", .(number_of_agents = uniqueN(Agent)), by = Agency], -number_of_agents)


ggplot(data = hills_agents_per_agency, aes(x= Agency, y = number_of_agents, order)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=25 )) +
  labs(x = "Hillsborough Agencies", y = "# of Agents in Proplogix data") +
  ggtitle("Top 20 Hillsborough Agencies by # of Agents seen in Proplogix data") +
  scale_x_discrete(limits = hills_agents_per_agency$Agency[1:20])



### Orders By County ###
 


prop_orders <- fread("C:/Users/trobart/Downloads/FL_FIPSCodes (1).csv")

# df_pop_county[region == prop_orders$FIPSCode, value := prop_orders$`Orders(LN)`]


county_choropleth(prop_orders, 
                  state_zoom = "florida",
                  title      = "PropLogix Job Counts (Raw) by County \n (Mar. 1st, 2016 - Feb. 1st, 2017)",
                  legend     = "Jobs",
                  num_colors = 1) + coord_map() 

county_choropleth(prop_orders, 
                  state_zoom = "florida",
                  title      = "PropLogix jobs (Log Scale) by County\n (Mar. 1st, 2016 - Feb. 1st, 2017)",
                  legend     = "Proportion of Jobs",
                  num_colors = 1) + 
  coord_map() + 
  scale_fill_gradient(
    high = 'green',
    low = 'white',
    trans="log",
    label = scales::log_breaks()
  )

OrdersByCounty <- fread('C:/Users/trobart/Downloads/tanner_queries.csv')
PaymentsByCounty <- fread('C:/Users/trobart/Downloads/tanner_queries4.csv')


OrdersByCounty[,region := County]
OrdersByCounty[,value := Payments]
OrdersByCounty[,County := NULL]
OrdersByCounty[,Payments := NULL]

OrdersByCounty$region <- factor(OrdersByCounty$region)

OrdersByCounty_ggplot <- county_choropleth(OrdersByCounty, aes(
  state_zoom = "florida",
  title      = "PropLogix Job Counts (Raw) by County \n (March, 2016 - March, 2017)",
  legend     = "Jobs",
  frame = c(Year, Month),
  num_colors = 1)) + coord_map() 

gganimate(OrdersByCounty_ggplot)

```
### Payments by Client ####

```{r}
PaymentsByClient <- fread('C:/Users/trobart/Downloads/tanner_queries3.csv') #load data

#split client field out into name and location
PaymentsByClient <- cSplit(PaymentsByClient, "Client", "- ")
PaymentsByClient[!is.na(Client_3),Client_2 := Client_3]
PaymentsByClient[,Location := Client_2]
PaymentsByClient[,Client := Client_1]
PaymentsByClient[,c("Client_1","Client_2", "Client_3") := NULL]



total_payments <- aggregate(Payments ~ Client, data = PaymentsByClient, FUN = sum)


sum(total_payments$Payments) # $6,628,077 (2016-2017)



sorted_client_payments <- total_payments[order(-total_payments$Payments),]
head(sorted_client_payments)


# raw revenue
ggplot(head(sorted_client_payments, 10)) + 
  geom_bar(stat = "identity") + 
  theme( axis.ticks.length = unit(.5, "cm"), axis.text.x= element_text(angle=25 )) + 
  aes(y = Payments, x = reorder(Client, -Payments), fill = Payments) +
  scale_y_continuous(labels = comma) +
  labs(y = "$ USD (Raw)", x = "Clients") +
  ggtitle("Total Revenue By Client (Top 10) (2016-2017)")


# percent of total revenue
ggplot(head(sorted_client_payments, 10), aes( x = reorder(Client, -Payments))) + 
  geom_bar(stat = "identity", aes( y = Payments/sum(total_payments$Payments), fill = Payments)) + 
  theme( axis.ticks.length = unit(.5, "cm"), axis.text.x= element_text(angle=25 )) + 
  scale_y_continuous(labels = comma) +
  scale_fill_continuous(low = "grey27", high = "green", limits= c(0,700000), label = comma) +
  labs(y = "%", x = "Clients", fill = "Range") +
  ggtitle("% PropLogix Revenue By Client (Top 10) (2016-2017)")
```
################################
##          Deed Plots          #
################################

#### plot of top 20 client agents by their raw counts in deed data

```{r}
deed_agent_counts <- as.data.frame(sort(table(reduced$`Title Agent`), decreasing = T)[1:20])


ggplot(data = deed_agent_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
  labs(x = "Deed Agents", y = "# of records in Deed data") +
  ggtitle("Top 20 Agents by raw Deed record counts") 
  #scale_x_discrete(limits = sort(table(reduced$`Title Agent`), decreasing = T)[1:20])


## plot of top 20 client agents by their proportion in deed data (pretty much identical to previous)

percent <- as.data.frame(sort(table(reduced$`Title Agent`), decreasing = T))$Freq/sum(as.data.frame(sort(table(reduced$`Title Agent`), decreasing = T))$Freq)

ggplot(data = deed_agent_counts, aes( x= Var1, y = percent[1:20])) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
  labs(x = "Deed Agents", y = "# of records in Deed data") +
  ggtitle("Top 20 Agents by raw Deed record counts") 
  #scale_x_discrete(limits = sort(table(reduced$`Title Agent`), decreasing = T)[1:20])
  
## plot of top 20 client agencies by their raw counts in deed data

deed_agency_counts <- as.data.frame(sort(table(reduced$`Title Company`), decreasing = T)[2:32])

deed_agency_counts <- deed_agency_counts[c(-1, -4, -8, -11, -13,-16:-20, -22, -26),] #removing junk rows


ggplot(data = deed_agency_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
  labs(x = "Deed Agencies", y = "# of records in Deed data") +
  ggtitle("Top 20 Agencies by raw Deed record counts")


## count of most agents per agency in deed data

deeds_agents_per_agency <- setorder(reduced[, .(number_of_agents = uniqueN(`Title Agent`)), by = `Title Company`], -number_of_agents)


ggplot(data = deeds_agents_per_agency[1:20], aes(x= `Title Company`, y = number_of_agents, order)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=90 )) +
  labs(x = "Hillsborough Agencies", y = "# of Agents in Proplogix data") +
  ggtitle("Top 20 Hillsborough Agencies by # of Agents seen in Proplogix data") +
  scale_x_discrete(limits = deeds_agents_per_agency$Agency)

```
##################################################
# Matched proplogix/deed records and exclusions  #
##################################################
```{r}

## top 20 counts of proplogix matched agents/agencies in the deed scraped data
hills_matched_counts # defined above
ggplot(data = hills_matched_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30)) +
  labs(x = "Hillsborough Clients", y = "# of prop matched records in deed data") +
  ggtitle("Top 20 Hillsborough Clients by raw job volume as matched to proplogix data")
```

## Top 20 deed agents in deed data explicitly NOT in the proplogix data agent names
```{r}
deed_agents_not_in_prop_agents_counts <- as.data.frame(sort(table(reduced[!(`Title Agent` %in% all_matched_records$`Title Agent`) ]$`Title Agent`), decreasing = T)[1:22])
deed_agents_not_in_prop_agents_counts <- deed_agents_not_in_prop_agents_counts[c(-6,-12),]
#| !(`Parcel ID Number` %in% all_matched_records$`Parcel ID Number`)
ggplot(data = deed_agents_not_in_prop_agents_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
  labs(x = "Deed Agents not in Prop Agents", y = "# of records in Deed data") +
  ggtitle("Top 20 Agents NOT in proplogix agents by raw Deed record volumes")

## Top 20 deed agents in deed data explicitly NOT in the proplogix agent names AND parcel IDs

deed_agents_not_in_prop_agents_and_parcels_counts <- as.data.frame(sort(table(reduced[!(`Title Agent` %in% all_matched_records$`Title Agent`) & !(`Parcel ID Number` %in% all_matched_records$`Parcel ID Number`) ]$`Title Agent`), decreasing = T)[1:21])
deed_agents_not_in_prop_agents_and_parcels_counts <- deed_agents_not_in_prop_agents_and_parcels_counts[-2,]
ggplot(data = deed_agents_not_in_prop_agents_and_parcels_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=25 )) +
  labs(x = "Deed Agents not in Prop Agents or Parcels", y = "# of records in Deed data") +
  ggtitle("Top 20 Agents NOT in proplogix agents and parcel IDs by raw Deed record volumes")



######    Redacted because only 2 items of the original deed list were present in prop data, not enough to make a meaningful comparison of proportion diffs
# 
# ## top 20 client agents by their proportion in deed data, compared beside the same clients proportions in prop data
# percent <- as.data.frame(sort(table(reduced$`Title Agent`), decreasing = T))$Freq/sum(as.data.frame(sort(table(reduced$`Title Agent`), decreasing = T))$Freq)
# prop_percent <- as.data.frame(sort(table(prop_jobs$Agent), decreasing = T))$Freq/sum(as.data.frame(sort(table(prop_jobs$Agent), decreasing = T))$Freq)
# 
# 
# ggplot(data = deed_agent_counts, aes( x= Var1, y = c(percent[1:20], prop_percent[1:20]))) + 
#   geom_bar(stat= "identity") +
#   theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
#   labs(x = "Deed Agents", y = "# of records in Deed data") +
#   ggtitle("Top 20 Agents by raw Deed record volumes") 



#################### warning poor data quality on following plot

deed_agencies_not_in_prop_agencies_counts <- as.data.frame(sort(table(reduced[!(`Title Company` %in% all_matched_records$`Title Company`) ]$`Title Agent`), decreasing = T)[1:25])
deed_agencies_not_in_prop_agencies_counts <- deed_agencies_not_in_prop_agencies_counts[c(-1, -3, -5, -7, -11, -19, -21 ),]

ggplot(data = deed_agencies_not_in_prop_agencies_counts, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
  labs(x = "Deed Agents not in Prop Agencies", y = "# of records in Deed data") +
  ggtitle("Top 20 Agents NOT in proplogix Agencies by raw Deed record volumes")

```


### Identifying the biggest cancellers, and seeing if we can check on the truth of the cancel in the deed data
```{r}

largest_cancels <- as.data.frame(sort(table(prop_jobs[Status == "Cancelled"]$Agency), decreasing = T)[1:20])

ggplot(data = largest_cancels, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
  labs(x = "Agencies", y = "# of Cancelled Jobs") +
  ggtitle("Top 20 Cancelling Agencies")


largest_cancels_in_deeds <- as.data.frame(sort(table(prop_jobs[PropertyId %in% parcel_reduced$`Parcel ID Number`][Status == "Cancelled"]$Agency), decreasing = T)[1:20])

ggplot(data = largest_cancels_in_deeds, aes( x= Var1, y = Freq)) + 
  geom_bar(stat= "identity") +
  theme( axis.ticks.length = unit(.3, "cm"), axis.text.x= element_text(angle=30 )) +
  labs(x = "Agencies", y = "# of cancelled properties in deed data") +
  ggtitle("Top 20 Cancelling Agencies where properties were found in deed data ")

cancelled <- prop_jobs[PropertyId %in% parcel_reduced$`Parcel ID Number`][Status == "Cancelled"]
parcel_reduced[(`Parcel ID Number` %in% cancelled$PropertyId) & (as.Date(`Date of Record`) > as.Date('2016-05-02'))]

cancelled[, `Parcel ID Number` := PropertyId]
new <- merge(cancelled, parcel_reduced, by = 'Parcel ID Number')

new[Agent == `Title Agent`]
new[Agency == `Title Company`]


#### Berlin patten cancels subset 
berlin_patten_cancels <- prop_jobs[PropertyId %in% parcel_reduced$`Parcel ID Number`][Status == "Cancelled"][Agency == "berlin patten ebling pllc"]
berlin_patten_cancels[, `Parcel ID Number` := PropertyId]
berlin_matched <- merge( berlin_patten_cancels, parcel_reduced, by = "Parcel ID Number")
berlin_matched[, `Instrument Number` := NULL]


write.csv(berlin_matched, "berlin_patten_cancels.csv")
```


#############################################################################
## Relationship network map of Proplogix client Title Agents and Agencies  ##
#############################################################################


```{r}
nodes <- as.data.frame(unique(unlist(list(unique(prop_jobs$Agent), unique(prop_jobs$Agency)))))

edges <- prop_jobs[, list(Freq = .N), by= list(Agent, Agency)]

visNetwork(nodes, edges, main = "Title Agents!")

net <- graph.data.frame(edges, nodes, directed = F)

net <- simplify(net, remove.multiple = F, remove.loops = T) 


# V(net)$color <- colrs[V(net)]
weights <- (edges$Freq)/sum(edges$Freq)
E(net)$width <- weights
l <- layout.fruchterman.reingold(net)

plot(net,vertex.label=NA, layout = l, rescale=F, vertex.size=12)

dg <- decompose.graph(net)



for (i in 1:length(dg)){
  
  l <- layout.fruchterman.reingold(dg[[i]])
  if (length(E(dg[[i]])) > 4){
    weights <- (edges$Freq)
    E(net)$width <- weights
    V(dg[[i]])[ degree(dg[[i]]) > 2]$color <- "red"
    V(dg[[i]])[ degree(dg[[i]]) <= 2]$color <- "gold"
    plot(dg[[i]], layout = l, vertex.size=15)
    }
}
```



#####################################################
## Relationship network map of the observed deed data 
#####################################################

```{r}
nodes <- unique(unlist(list(unique(reduced$`Title Company`), unique(reduced$`Title Agent`))))

edges <- reduced[, list(Freq = .N), by= list(`Title Company`, `Title Agent`)]

net <- graph.data.frame(edges, nodes, directed = F)

# net <- simplify(net, remove.multiple = F, remove.loops = T)  #reduces the network by removing self-loops and redundant connections


weights <- (edges$Freq)/sum(edges$Freq)
E(net)$width <- weights
l <- layout.fruchterman.reingold(net)

plot(net,vertex.label=NA, layout = l, rescale=F, vertex.size=12)

dg <- decompose.graph(net)



for (i in 1:length(dg)){
  
  l <- layout.fruchterman.reingold(dg[[i]])
  if (length(E(dg[[i]])) > 3){
    weights <- (edges$Freq)
    E(net)$width <- weights
    V(dg[[i]])[ degree(dg[[i]]) > 2]$color <- "red"
    V(dg[[i]])[ degree(dg[[i]]) <= 2]$color <- "gold"
    plot(dg[[i]], layout = l, vertex.size=15)
    }
}
```
